---
title: "homework4"
author: "Marco Dodson"
date: "2024-04-23"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=TRUE,result='asis'}
##load packages
library(knitr)
###settings for R chunks
knitr::opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning = TRUE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output # nolint
```

# Question 8 
## (A): Determine the simulation size with an error tolerance of 50 cents 
### let's use n = (z * σ / ε)^2
```{r}
set.seed(123)
n_init <- 10^4 
x_init <- runif(n_init, min = 0, max = 2)
z_init <- 2 * 1000 * (1/10) * exp(-x_init/10)
sd_init <- sd(z_init)

epsilon <- .05
Z <- 1.96
n_req <- ceiling((Z * sd_init / epsilon)^2)
cat("Required sample size:", n_req, "\n")

```

### (B): I think the sample size I had in problem 4 (d) was 2255413 so this required sample is less 13.59x less to be exact


```{r}
mean_z <- mean(z_init)

ci_lower <- mean_z - 1.96 * sd_init / sqrt(n_req)
ci_upper <- mean_z + 1.96 * sd_init / sqrt(n_req)
cat("95% confidence interval: [", ci_lower, ",", ci_upper, "]\n")
```

## (C): looks like it doesn't contain the true answer -  181.2692



# Problem 9:
## (A): derive the inverse function,  F^(-1) of the CDF F(x) = 1 - (2/x)^3, x ≥ 2:
### Let y = F(x) = 1 - (2/x)^3
### Solve for x in terms of y:
### 1 - y = (2/x)^3
### (1 - y)^(1/3) = 2/x
### x = 2 / (1 - y)^(1/3)
### F^(-1)(y) = 2 / (1 - y)^(1/3), 0 ≤ y < 1.

## (B): generate 10 instaces from F(x) using invesrse distribtution transformation method
```{r}
N <- 10 
u <- runif(N)
x <- 2 / (1-u)^(1/3)
cat("10 instances: [", x,"]\n")
```
