---
title: "in-classLab1"
author: "Marco Dodson"
date: "2024-04-02"
output: html_document
---
---
```{r echo=FALSE,message=FALSE,warning=TRUE,result='asis'}
##load packages
library(knitr)
###settings for R chunks
knitr::opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning = TRUE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output # nolint
```

## (b) Delete all existing variables first.

```{r}
rm(list=ls()) # Remove all variabls from the environment
```

## (c) Create an nxd matrix to record the numbers of d people for n games 

```{r}
n=3 # number of games 
d=5 # number of people 
game.numbers=matrix(NA,nrow = n,ncol=d) # create empty matrix to store the numbers 
```

## (d) Assign the leftmost person with a random number on [0,1].

```{r}
game.numbers[,1]=runif(n) # assign random numbers of first column of matrix 
```

## (e) Assign numbers to the rest of people in n games.

```{r}
for(i in 2:d) { # loop through columns 2 to d 
    game.numbers[,i]=(game.numbers[,i-1] + runif(n))/2 # compute the average of the prev number and random new number
}
```

## (f) Record the winning (1) or losing (0) of each row (game).

```{r}
game.results=apply(game.numbers,1,function(x)any(x>.6)) # check if any number in each row is greater than .6 
game.results=as.integer(game.results) # convert the logical values to integers 
```

## (g) Count the number of times that we win.

```{r}
number.wins=sum(game.results) #sum up the number of wins 1's in game.results
```

## (h) Compute the estimated probability.

```{r}
n<-10000 # increase the number of games to 10,000 for accurate estimate 
game.numbers=matrix(NA,nrow=n,ncol=d) # create new matrix for larger number of games 
game.numbers[,1]=runif(n) # assign random numbers of first column of matrix 
for(i in 2:d){ # loop through columns 2 to d 
    game.numbers[,i]=(game.numbers[,i-1] + runif(n))/2 # compute the average of the prev number and random new number
}
game.results=apply(game.numbers,1,function(x)any(x>.6)) # check if any number in each row is greater than .6 
game.results=as.integer(game.results) # convert the logical values to integers 
est.prob=sum(game.results)/n # estimate probability of winning 
```

## (i) Compute the confidence interval.

```{r}
CI.low=est.prob-2.58*sqrt(est.prob*(1-est.prob)/n) # lower bounds 
CI.high=est.prob+2.58*sqrt(est.prob*(1-est.prob)/n) # upper bounds 
```

We are 99% confident that the probability of winning the game falls between ``r CI.low`` and ``r CI.high``
The estimated probability of winning the game is ``r est.prob``.

## The result should change each time the program is run becuse the numbers are generated randomly. The Monte Carlo method relies on generating a large number of random samples to estimate the probability. each run generates a new set of random numbers. 