---
title: "inclasslab5"
author: "Marco Dodson"
date: "2024-04-30"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=TRUE,result='asis'}
##load packages
library(knitr)
###settings for R chunks
knitr::opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning = TRUE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output # nolint
```

## (1): 
### The target distribution's pdf is fX(x) = 6x(1 - x), 0 ≤ x ≤ 1. 
### The candidate distribution's pdf is fZ(z) = 1, 0 ≤ z ≤ 1. To find the efficiency, we need to calculate:
### c = 1 / max(fX(x) / fZ(x))
### The maximum value of fX(x) / fZ(x) occurs at x = 0.5:
### fX(0.5) / fZ(0.5) = 6 * 0.5 * (1 - 0.5) / 1 = 1.5
### c = 1 / 1.5 = 2/3 ≈ 0.6667.


## (2): Since 0 < c ≤ 1, U[0,1] is a valid candidate distribution

### Define the constants

```{r}
rm(list=ls())
n = 10000
c = 2/3
```

### Compute the numger of candidate numbers

```{r}
N = ceiling(n/c*1.1)
```

### Generate candidate numbers and criterion numbers

```{r}
z = runif(N)
w = runif(N)
```

### Acceptance-rejection procedure

```{r}
accept.index = which(w <= 4*z**(1-z))
prex = z[accept.index]
x = prex[1:n]
```

### Plot the histogram of the generated numbers and compare with the target distribution.

```{r}
hist(x, main="Historgram of Generated Numbers", prob=TRUE, ylim=c(0,1.5))
xfit = seq(0,1,length.out = 100)
lines(xfit, 6*xfit*(1-xfit), col="red", lwd=2)
```

[Since the histogram follows the target density curve, this indicates the numbers are indeed drawn from the target distribution]
