---
title: "In-ClassLab2"
author: "Marco Dodson"
date: "2024-04-10"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```

## 1. 
### (a) [the target random variable y is the payout ofthe life insurance policy which is 50000 if life insurance dies within 20 years otherwise 0]

### (b) [the basic random variable x is the survival time of the insured which follows an exponential distribution with mean of 25 years]

### (c) [the function f to link x and y is y = f(x) = {50000 if x < 20 } {0 if x >= 20}]

### (d) [the fair premium is the expected value of y, e(y)]

## 2. [generate large sample of survival times from exponential distribtion, apply the function f to each x to obtain samples of y, estimate the fair premium by calculating sample mean of y, then provide 99% confidence level]

## 3.
### (a) 
```{r}
n = 1000
x = rexp(n, rate = 1/25)
```

### (b)
```{r}
y = ifelse(x < 20, 50000, 0)
```

### (c)
```{r}
est.premium = mean(y)
```

### (d)
```{r}
est.error = 2.58 * sd(y) / sqrt(n)
```

### (e) [The estimated fair premium based on a sample size of 1000 is $`r round(est.premium, 2)` with a 99% confidence interval of +/- $`r round(est.error, 2)`]

## 4. 
```{r}
n = 1000
x.initial = rexp(n, rate = 1/25)
y.initial = ifelse(x.initial < 20, 50000, 0)
hat.sigma = sd(y.initial)
epsilon = 5
c = 1.2
N = ceiling((2.58 * c * hat.sigma / epsilon)^2)
```
The required sample size is ``r N ``.

## 5.
```{r}
x = rexp(N, rate = 1/25)
y =  ifelse(x < 20, 50000, 0)
est.premium = mean(y)
est.error = 2.58 * sd(y) / sqrt(N)
```
[Based on the required sample size of `r N`, the estimated fair premium is $`r round(est.premium,2)` with a 99% confidence interval of +/- $`r round(est.error,2)`. This has a error tolerance of $5, meaning true price is likely 5 within the estimated value. ]


