---
title: "In-ClassLab6"
author: "Yiou Li"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=FALSE,
               results='asis') #echo: whether prints the R code; message: whether shows the message outputs; warning: whether shows the warning messages; results: whether contain ## in front of the R output; fig.keep: show all figures or just the last one in an R chunk
```

### 1. [Insert your answer here.]

### 2. [Insert your answer here.]

### 3. 

Define the simulation size.

```{r}
rm(list=ls())
n =
```

Our goal is to generate a sample of game results. Thus, create vectors to store the sampled door numbers and game results.

```{r}
car.door = c() #the door numbers with the car
player.door = c() #the door numbers the player chooses
host.open = c() #the door numbers the host opens
player.final = c() #the door numbers the player finally switches to
game.result=c()
```


For each one of the $n$ games, we need to repeat the steps described in the in-class lab 6 document. The simplest way to do this is to use a "for loop". We use "i" to denote the numbering of the game. 

```{r}
for (){
  ### randomly pick a door for the car
  car.door[i] = sample()
  ### the player randomly pick a door
  player.door[i] = sample()
  ### the host opens a door with a goat. There are two scenarios.
    if (){
      available.doors = setdiff()
      host.open[i] = sample()
    } else{
      host.open[i] = setdiff()
    }
  ### player switches the door
  player.final[i] = setdiff()
  ### the result of the ith game
  game.result[i] = ifelse()
}
```

### 4. 99% confidence interval of true probability/proportion is
$$\hat{p}\pm 2.58\sqrt{\frac{\hat{p}(1-\hat{p})}{n}}.$$

```{r}
est.prob = 
est.error = 
CI.low = 
CI.high = 
CI.low
CI.high
```

### 5. [Insert your answer here.]