---
title: "Lecture Note 7 Sample Code"
author: "Yiou Li"
output: html_document
---

```{r echo=FALSE,message=FALSE,warning=FALSE}
# Load the packages
library(knitr)
library(scales) #to use percent function
###settings for R chunks
opts_chunk$set(echo=TRUE,
               message=FALSE,
               warning=TRUE,
               results='asis') 
```


### Example. Quiz score problem. Estimate mean quiz 3 score using quiz 2 score as the control variate.

```{r}
rm(list = ls()) #clear the workspace
#define the constants
n=10^4
#generate instances of quiz 2 score
x = sample(c(2,4,6,8),n,replace=TRUE)
mu.x = 5 #true mean of x
#generate the fluctuations of quiz 3
v = sample(c(-2,0,2),n,replace=TRUE)
#generate instances of quiz 3 score
y = x+v
#calculate hat(beta)
hat.beta = cov(x,y)/var(x)
#calculate w_i's
w = y+hat.beta*(mu.x-x)
#Monte Carlo estimation using control variate
est.CV = mean(w)
#true error
true.error.CV = abs(5-est.CV)

#comparison with simple Monte Carlo estimator
est.SMC = mean(y)
true.error.SMC = abs(5-est.SMC)
```
With simulation size n=``r n`` ,the estimated mean Quiz 3 score is ``r est.SMC`` using simple Monte Carlo estimation, with a true error of ``r true.error.SMC``. Using Quiz 2 score as the control variate, the estimated mean Quiz 3 score is ``r est.CV``  with a true error of ``r true.error.CV``.

### Example. Estimate Asian geometric mean call option price using the discounted payoff of the European call option as the control variate.

```{r}
rm(list=ls()) #clear the variables
source('Sample.GBM.R') # source the code to generate sample paths of GBM
source('ExactPrice.GBM.R') #source the code to compute B-S prices

#define the constants
S.0 = 120
K = 125
MT=1/4 #3-month option
r=0.05
sigma=0.26
d=3  # #of times monitered during the contract
n=10^3 # sample size
#exact price of European call option calculated using Black-Scholes formula. This is the mean of control variate (mu_X).
ExactEuroCall.price=ExactPrice.GBM(S.0,MT,r,sigma,K,'call')

#generate sample paths
S = Sample.GBM(S.0,MT,r,sigma,d,n)
#generate discounted payoffs of European call option, i.e., generate samples of control variate, X.
EuroCallPayoff=pmax(S[,d]-K,0)*exp(-r*MT)
#generate discounted payoffs of geometric mean call option, i.e., generate samples of target random variable, Y.
GeoMean=apply(S^(1/d),1,prod) #You must use the sample paths for European option and Asian option to create correlation!!!!!
GeoCallPayoff=pmax(GeoMean-K,0)*exp(-r*MT)
#calculate hat_beta
hat.beta=cov(GeoCallPayoff,EuroCallPayoff)/var(EuroCallPayoff)
#compute w_i's
w = GeoCallPayoff+hat.beta*(ExactEuroCall.price-EuroCallPayoff)
#estimate geometric mean call option price using control variate
GeoCall.CV = mean(w) 

#compute exact price of Asian geometric mean call option, true value of E(Y)
BarT=MT*(1+1/d)/2
Barsigma=sqrt(sigma^2*(2+1/d)/3)
Barr=r+(Barsigma^2-sigma^2)/2
ExactGeoCall.price=ExactPrice.GBM(S.0,BarT,Barr,Barsigma,K,'call')*exp(Barr*BarT-r*MT)
# compute the true error of estimate using control variate
true.error.CV = abs(ExactGeoCall.price-GeoCall.CV)

#compare to simple Monte Carlo estimator
GeoCall.SMC = mean(GeoCallPayoff) 
true.error.SMC = abs(ExactGeoCall.price-GeoCall.SMC)

```
With initial asset price of ``r dollar(S.0)`` , risk-free rate of ``r percent(r,accuracy=0.01)`` , volatility of ``r percent(sigma,accuracy=0.01)``, maturity time of ``r MT`` years, strike price ``r dollar(K)``, asset price monitored ``r d`` times, and simulation size of ``r n``, the simple Monte Carlo estimate of Geometric Mean Asian call option price is ``r dollar(GeoCall.SMC)``, with a true error of ``r dollar(true.error.SMC)``. Using European call discounted payoff as control variate, the Monte Carlo estimate  of Geometric Mean Asian call option price is ``r dollar(GeoCall.CV)``, with a true error of ``r dollar(true.error.CV)``. 
